Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-10 documentation/paper.tex
Added results table for ImageConv

Throughout a variety of different network architectures, the best validation accuracy obtained was 85\%. The corresponding training accuracy of 100\% indicates that severe overfitting is taking place. Also, the class-wise standard deviation was a very high 0.95, which implies its decisions are nearly random (as is apparent in \ref{image_window}). It is likely fitting on some form of noise within $\iota$. The fact that throughout many trials (including a grid search), no good performance on validation data was observed, provides significant evidence that images provide insufficient information for effective discrimination.

@@

The following tables compare the accuracy and mean class-wise standard deviation values of various supervised learning configurations with multiple input formats, with Acoustic Parameter and the original PICO-60 neural network provided as baselines.

>>>>

Throughout a variety of different network architectures, the best validation accuracy obtained was a deceptively high 85\%. The corresponding training accuracy of 100\% indicates that severe overfitting is taking place. Also, the class-wise standard deviation was a very high 0.95, which implies its decisions are nearly random (as is visually apparent in \ref{image_window}). It is likely fitting on some form of noise within $\iota$. The fact that throughout many trials (including a grid search), no good performance on validation data was observed, provides significant evidence that images provide insufficient information for effective discrimination.

The following table shows performance of various configurations of $ImageConv(\iota)$:

\begin{tabular}{|l|l|l|l|l|l|}
    \hline
    L2 $\lambda$ & Dropout & Convolutional Layers & Dense Layers & Max Accuracy & Class-Wise Std Dev \\
    \hline
    0 & 0.5 & 4 & 3 & 77\% & 1.01 \\
    \hline
    0 & 0.25 & 4 & 3 & 85\% & 0.95 \\
    \hline
    0.01 & 0.25 & 4 & 3 & 66\% & 0.97 \\
    \hline
    0.003 & 0.25 & 4 & 3 & 69\% & 0.97 \\
    \hline
    0.01 & 0.25 & 12 & 3 & 66\% & 0.98 \\
    \hline
    0.01 & 0.5 & 12 & 3 & 68\% & 0.99 \\
    \hline
\end{tabular}

@@

The following tables compare the accuracy and mean class-wise standard deviation values of certain highlight supervised learning configurations with multiple input formats, with Acoustic Parameter and the original PICO-60 neural network provided as baselines.
